---
title: "Snake Countries Walkthrough - With Selenium"
output: html_notebook
---

So at the end of my last attempt, I'd come up against what I thought would be just a little issue, but turns out it was more than I was expecting.

The individual country pages would have multiple tables spread across multiple pages, with javascript links in between. My hope was I could just select those with rvest, but it wasn't to be.

So instead the new approach is to use rSelenium, an r package for an automated browser (selenium), to access this. However to do so I need to use docker, and this involved a bit of mindless clicking.

So I downloaded docker from their website, and selenium from theirs.
I installed rselenium and followed it's instructions for someone who doesn't understand docker/any of this, and used the instruction `RSelenium::rsDriver()`

https://cran.r-project.org/web/packages/RSelenium/vignettes/RSelenium-basics.html

```{r}
library(RSelenium)
library(tidyverse)
# RSelenium::rsDriver()
```

I set up a docker machine by going into the terminal (nice and easy in rstudio)
`docker run -d -p 4445:4444 selenium/standalone-chrome`

To then find out any details about it I ran

`docker ps`

This brings up a table showing it's:

- Container ID
- Image
- Command
- Created
- Status
- Ports
- Names

```{r docker}
remDr <- RSelenium::remoteDriver(remoteServerAddr = "localhost",
                      port = 4445L,
                      browserName = "chrome")
remDr$open()
```

I don't understand this, but it seems to be working, we can navigate to the website inside our browser
```{r selenium_navigate}
remDr$navigate("http://apps.who.int/bloodproducts/snakeantivenoms/database/SearchFrm.aspx")
remDr$screenshot(display = TRUE)
```

Can we use rvest to download stuff from what we've just created? Yes! We can!
```{r download_country_list}
snake_countries <- xml2::read_html(remDr$getPageSource()[[1]]) %>%
  rvest::html_nodes("#ddlCountry") %>%
  rvest::html_children() %>%
  rvest::html_attr("value") %>%
  dplyr::data_frame(countries = .)

# snake_countries <- snake_countries[-1,]
snake_countries <- snake_countries %>%
  dplyr::mutate(list_position = 1:160)
```

So now we want to navigate with selenium to a country page?

```{r load_malawi}
#Now this is doing something different, its working down the list and selecting countries. Malawi is the 85'th country on the list alphabetically

element<- remDr$findElement(using = 'css selector', "#ddlCountry > option:nth-child(85)")
element$clickElement()

remDr$screenshot(display = TRUE)
```

```{r extract_malawi}
html <- xml2::read_html(remDr$getPageSource()[[1]])
xml2::write_html(html, "malawi.html")
```

So then what we want to do is use the javascript links we found to load the next page

```{r malawi_page_two}
element <- remDr$findElement(using = 'css selector', "#SnakesGridView > tbody > tr:nth-child(12) > td > table > tbody > tr > td:nth-child(2)")
element$clickElement()
remDr$screenshot(display = TRUE)
```

Success!

Now there's just a couple of things left to do.

Download the snake information from the first page of a country profile and store it as a dataframe [x]
Identify whether there is a second/third/fourth page for the profile
Go to these pages and download them [x]

Iterate this process like we did for snake profiles, to work through the whole database.

So first things first. There will be a clever way to do this in RSelenium, but we've created a method that works with RVest, so let's just do that again.

It looks like we want a dataframe that collects:

- Link
- Category 
- Common Name
- Species Name

```{r malawi_download}
country_html <- xml2::read_html(remDr$getPageSource()[[1]])

country_table <- country_html %>%
  rvest::html_node("#SnakesGridView") %>%
  rvest::html_table(fill = TRUE)

# Then we add a mutate statement to add the name of the country we want
```

Right, the fact that the links to other pages for the same country, are in this table isn't a disaster. In fact it allows us to work out if a country has multiple pages or not.

If a country has a single page, the html table created has four columns.
If it has multiple pages, the html table has 6, as the links mess things up.
So we could put the whole thing into an ifelse statement.

If length of the table is 4, do this, if 6, do that.

So let's build our first attempt at starting from the beginning, to download a country profile.

```{r download_country}
# First Load Our Browser
remDr <- RSelenium::remoteDriver(remoteServerAddr = "localhost",
                      port = 4445L,
                      browserName = "chrome")
remDr$open()

# Then Go To Our Country
remDr$navigate("http://apps.who.int/bloodproducts/snakeantivenoms/database/SearchFrm.aspx") # First we load the databas
element<- remDr$findElement(using = 'css selector', "#ddlCountry > option:nth-child(85)")
element$clickElement() #We'll need to create a way to insert the country into that child form

# Then Extract The Snake Page
country_html <- xml2::read_html(remDr$getPageSource()[[1]])

country_table <- country_html %>%
  rvest::html_node("#SnakesGridView") %>%
  rvest::html_table(fill = TRUE)

# Then Determine If There Are More Pages
more_pages <- length(country_table) > 4

snake_country_secondary_download <- function(page_element){
  
  element <- remDr$findElement(using = 'css selector', page_element)
  element$clickElement()
  
  country_html <- xml2::read_html(remDr$getPageSource()[[1]])
  
  secondary_country <- country_html %>%
  rvest::html_node("#SnakesGridView") %>%
  rvest::html_table(fill = TRUE)
  
  secondary_country
}

if(more_pages == TRUE){
  # Then Work Out Exactly How Many More Pages
  country_table_number <- country_html %>%
  rvest::html_node("#SnakesGridView") %>%
  rvest::html_node("tbody > tr:nth-child(12)") %>%
  rvest::html_node("td") %>%
  rvest::html_node("table") %>%
  rvest::html_node("tr") %>%
  rvest::html_nodes("td") %>%
  length()

  
  country_pages <- dplyr::data_frame(
    page_number = 1:country_table_number,
    page_element = stringr::str_c("#SnakesGridView > tbody > tr:nth-child(12) > td > table > tbody > tr > td:nth-child(", page_number, ")"))
  
  country_pages <- country_pages[-1,]
  country_pages <- country_pages[,2]
    
  secondary_country <- purrr::pmap(country_pages, snake_country_secondary_download) %>%
  dplyr::bind_rows()
  
  country_table <- dplyr::bind_rows(country_table, secondary_country)
  country_table <- country_table[,1:4] %>%
    dplyr::filter(is.na(`Link*`))
}
```

The above code can be put into a download country function.

So now all we need is a couple more things.

Our script will need to create a list of countries, with their:
- Name
- ID
- Position in List

```{r create_country_list}
remDr$navigate("http://apps.who.int/bloodproducts/snakeantivenoms/database/SearchFrm.aspx")

snake_countries <- xml2::read_html(remDr$getPageSource()[[1]]) %>%
  rvest::html_nodes("#ddlCountry") %>%
  rvest::html_children() %>%
  rvest::html_attr("value") %>%
  dplyr::data_frame(country_id = .)

snake_country_names <- xml2::read_html(remDr$getPageSource()[[1]]) %>%
  rvest::html_nodes("#ddlCountry") %>%
  rvest::html_children() %>%
  rvest::html_text()

snake_countries <- snake_countries %>%
  dplyr::mutate(list_position = 1:160,
                country_name = snake_country_names,
                x = stringr::str_c("#ddlCountry > option:nth-child(",list_position, ")"))

# We chop off our first one as we are never going to navigate to there
snake_countries <- snake_countries[-1,]
```

This all seems to be working! Just the last stages now. We'll put the above example into a function.
We've now created two functions: snake_country_secondary_download, and snake_country_download.

```{r snake_country_download}
#' This function is used by the snake_country_data script, to create a data_frame listing all countries and the snakes they contain
#'
#' @param x the address for selenium to find the next country
#' @param country_id the ID WHO uses for countries
#' @param country_name the name of the country
#' @importFrom magrittr "%>%"
#' @export
#' @examples
#' snake_country_download()

snake_country_download <- function(x, country_id, country_name){
  # Then Go To Our Country
  remDr$navigate("http://apps.who.int/bloodproducts/snakeantivenoms/database/SearchFrm.aspx") # First we load the databas
  element<- remDr$findElement(using = 'css selector', x)
  element$clickElement() #We'll need to create a way to insert the country into that child form
  
  # Then Extract The Snake Page
  country_html <- xml2::read_html(remDr$getPageSource()[[1]])
  
  country_table <- country_html %>%
    rvest::html_node("#SnakesGridView") %>%
    rvest::html_table(fill = TRUE)
  
  # Then Determine If There Are More Pages
  more_pages <- length(country_table) > 4
  
  if(more_pages == TRUE){
    # Then Work Out Exactly How Many More Pages
    country_table_number <- country_html %>%
      rvest::html_node("#SnakesGridView") %>%
      rvest::html_node("tbody > tr:nth-child(12)") %>%
      rvest::html_node("td") %>%
      rvest::html_node("table") %>%
      rvest::html_node("tr") %>%
      rvest::html_nodes("td") %>%
      length()
    
    # Then create a data frame, with new address from us to download these from
    country_pages <- dplyr::data_frame(
      page_number = 1:country_table_number,
      page_element = stringr::str_c("#SnakesGridView > tbody > tr:nth-child(12) > td > table > tbody > tr > td:nth-child(", page_number, ")"))
    
    country_pages <- country_pages[-1,]
    country_pages <- country_pages[,2]
    
    # Then use a secondary function to download these
    secondary_country <- purrr::pmap(country_pages, snake_country_secondary_download) %>%
      dplyr::bind_rows()
    
    # Then, for countries that we had to download multiple pages, merge them all together
    country_table <- dplyr::bind_rows(country_table, secondary_country)
    country_table <- country_table[,1:4] %>%
      dplyr::filter(is.na(`Link*`))
  }
  
  country_table <- country_table %>%
    dplyr::mutate(country_id = country_id,
           country_name = country_name)
  
  message(country_name)
  country_table
}
```



```{r last_steps}
afghanistan <- snake_country_download(x = snake_countries$x[1], country_id = snake_countries$country_id[1], country_name = snake_countries$country_name[1])
```

Lets test it with a minisample
```{r final_test}
mini_countries <- head(snake_countries) %>%
  dplyr::select(-list_position)

mini_data <- purrr::pmap(mini_countries, snake_country_download) %>%
  dplyr::bind_rows()
```

That works too!
