---
title: "Country Profiles"
output: html_notebook
---

```{r library}
library(snakes)
```

Firstly we need to load up the database and select the country tag:

```{r download_country_list}
snake_countries <- xml2::read_html("http://apps.who.int/bloodproducts/snakeantivenoms/database/SearchFrm.aspx") %>%
  rvest::html_nodes("#ddlCountry") %>%
  rvest::html_children() %>%
  rvest::html_attr("value") %>%
  dplyr::data_frame(countries = .)

snake_countries <- snake_countries[-1,]
```

So now we need to see if we can load up the database and load up an individual country, 85 is the ID for India:

```{r load_single_country}
  country <- rvest::html_session("http://apps.who.int/bloodproducts/snakeantivenoms/database/SearchFrm.aspx")
  
  # Load up their query form, create the input we want, and download the species page
  country_form <- rvest::html_form(country)[[1]]
  country_form_submit <- rvest::set_values(country_form, ddlCountry = "85")
  country_zero <- rvest::submit_form(country, country_form_submit) %>%
    xml2::read_html()
  
  # Then let's have a look at the form
  xml2::write_html(country_zero, "country.html")
```

So the confusing bit for me here is the fact that a country may be split up over several pages. That's why we picked India in the first place, knowing it has loads of snakes.

We'd hope the links to the next pages would be in a standalone table with it's own name, so they could be referenced directly. But no. They're not.

So instead we'll need to select that table and work out how to extract the links afterwards. We know that the country page will show ten snakes and then split.

This turned out to be a bit more difficult for me than hoped as the bottom row of the table, wasn't named and I wasn't sure how to specify it. I turned to google and this article: http://bradleyboehmke.github.io/2015/12/scraping-html-tables.html. This had a lot of useful information, and it allowed me to think of using the `xml2::xml_child()` function to select the twelth row of a table. The logic is:

- When a table has more than ten snakes on it's first page it will have links to following pages
- So it will have twelve xml children (the eleventh is just buffer)
- If we drill down into that twelth row we can work out how many additional pages there are
- Using the length argument we can extract the amount of pages of snakes for each country

Doing something similar, just drilling a bit further down, we can extract the links for the next two pages.


```{r extract_country_snakes}
country_table_number <- country_zero %>%
  rvest::html_node("#SnakesGridView") %>%
  xml2::xml_child(12) %>%
  rvest::html_node("td") %>%
  rvest::html_node("table") %>%
  rvest::html_node("tr") %>%
  rvest::html_nodes("td") %>%
  length()

country_table_links <- country_zero %>%
  rvest::html_node("#SnakesGridView") %>%
  xml2::xml_child(12) %>%
  rvest::html_node("td") %>%
  rvest::html_node("table") %>%
  rvest::html_node("tr") %>%
  rvest::html_nodes("td") %>%
  rvest::html_nodes("a") %>%
  rvest::html_attr("href")
```

Can we actually use these links to then go to the next page of snake information?

```{r country_second_page}
  country <- rvest::html_session("http://apps.who.int/bloodproducts/snakeantivenoms/database/SearchFrm.aspx")
  
  # Load up their query form, create the input we want, and download the species page
  country_form <- rvest::html_form(country)[[1]]
  country_form_submit <- rvest::set_values(country_form, ddlCountry = "85")
  country_zero_plus_one <- rvest::submit_form(country, country_form_submit) %>%
  rvest::jump_to(country_table_links[1])
```

No. Turns out we can't. There's an error there that I think is just because I'm trying to get it to submit javascript and it can't just follow it like a link.

After a bit of googling it looks like everyone recommends using RSelenium for things like this.

So after loading up an article about this on [cran](https://cran.r-project.org/web/packages/RSelenium/vignettes/RSelenium-basics.html) we go to the selenium website and download the [server](http://docs.seleniumhq.org/download/).

Then it wan't us to use Docker, something I haven't tried before. So I'm going to do as little as possible, and use the function `rsDriver`

`install.packages("RSelenium")`

At this point it got very confusing, so I need a new markdown notebook.
